---
title: "Case Study 1 - (Retail)"
author: "Mayur Kastiya"
output: html_document
---

------------------------------------------------------

Q1. Merge the datasets Customer, Product hierarchy and Transactions as Customer_Final. Ensure to keep all customers who have done transaction with us and select the join type accordingly.

```{r}
Customer <- read.csv("E:/My Photo/Analytics/R_Bangalore/R Case Studies (All 3 case studies)/R case study 1 (Retail)/Customer.csv")

Transactions <- read.csv("E:/My Photo/Analytics/R_Bangalore/R Case Studies (All 3 case studies)/R case study 1 (Retail)/Transactions.csv")

prod_cat_info <- read.csv("E:/My Photo/Analytics/R_Bangalore/R Case Studies (All 3 case studies)/R case study 1 (Retail)/prod_cat_info.csv")
```

Re-naming prod_sub_cat_code column in prod_cat_info table to make it similar to transaction table

```{r}
#install.packages("dplyr")
require(dplyr)
prod_cat_info <- dplyr::rename(prod_cat_info, "prod_subcat_code" = "prod_sub_cat_code")
head(prod_cat_info,2)
```

a) Use the Base Merge()

merge(x = Transactions,
      y = prod_cat_info,
      by.x = "prod_cat_code",
      by.y = "prod_cat_code",
      all.x = TRUE
) -> Temp_table

merge(x = Temp_table,
      y = Customer,
      by.x = "prod_cat_code",
      by.y = "prod_cat_code",
      all.x = TRUE
) -> Customer_Final


b) Dplyr merge functions

```{r}
#install.packages("dplyr")
Temp <- dplyr:: left_join(Transactions,prod_cat_info,by= c("prod_cat_code","prod_subcat_code"))
Customer_Final <- dplyr:: left_join(Temp,Customer,by= c("cust_id" = "customer_Id"))
```

Converting "DOB" and "tran_date" from Factor type to Date type

```{r}
Customer_Final$DOB <- as.Date(Customer_Final$DOB, format="%d-%m-%Y")
a <- as.Date(Customer_Final$tran_date, format="%d-%m-%Y")
b <- as.Date(Customer_Final$tran_date, format="%d/%m/%Y")
a[is.na(a)] <- b[!is.na(b)]
Customer_Final$tran_date <- a
```

Removing duplicate rows

```{r}
Customer_Final <- Customer_Final[!duplicated(Customer_Final),]
```

Q2. Prepare a summary report for the merged data set.

a) Get the coloumn names and their corresponding data types

```{r}
str(Customer_Final)
```

b) Top/Bottom 10 Observations

Top 10 observations

```{r}
head(Customer_Final,10)
```

Bottom 10 observations

```{r}
tail(Customer_Final,10)
```

c) "Five number summary" for continuous variables (min,Q1,median,Q2,max)

```{r}
summary(Customer_Final)
```

d) Frequency table for all the categorical variables

```{r}
#install.packages("plyr")
require(plyr)
count(Customer_Final, "Gender")
```

```{r}
count(Customer_Final, "Store_type")
```

```{r}
count(Customer_Final,"prod_cat")
```

```{r}
count(Customer_Final, "prod_subcat")
```

Q3. Generate histograms for all continuous variables and frequency bars for categorical variables

Histogram for all continuous variables

```{r}
#install.packages('ggplot2')
require(ggplot2)
h3 <- ggplot(data=Customer_Final) + aes(x= Qty) + geom_histogram(bins=5, fill ="blue", color = "black")
h3
```

```{r}
h4 <- ggplot(data=Customer_Final) + aes(x= Rate) + geom_histogram(bins=5, fill ="blue", color = "black")
h4
```

```{r}
h5 <- ggplot(data=Customer_Final) + aes(x= Tax) + geom_histogram(bins=5, fill ="blue", color = "black")
h5
```

```{r}
h6 <- ggplot(data=Customer_Final) + aes(x= total_amt) + geom_histogram(bins=5, fill ="blue", color = "black")
h6
```

Frequency Bars for Categorical Variables

```{r}
require(magrittr)
b1_count <- Customer_Final %>% dplyr::filter(Gender=="M" | Gender=="F") %>% dplyr::group_by(Gender) %>% dplyr::summarise(Count = n())
b1 <- ggplot(data = b1_count) + aes(x= Gender, y= Count) + geom_bar(stat = "identity", color = "black", fill = "darkgreen")
b1
```


```{r}
#require(magrittr)
b2_count <- Customer_Final %>% dplyr::group_by(Store_type) %>% dplyr::summarise(Count = n())
b2 <- ggplot(data = b2_count) + aes(x= Store_type, y= Count) + geom_bar(stat = "identity", color = "black", fill = "darkgreen")
b2
```

```{r}
#require(magrittr)
b3_count <- Customer_Final %>% dplyr::group_by(prod_cat) %>% dplyr::summarise(Count = n())
b3 <- ggplot(data = b3_count) + aes(x= prod_cat, y= Count) + geom_bar(stat = "identity", color = "black", fill = "darkgreen")
b3
```

```{r}
b4_count <- Customer_Final %>% dplyr::group_by(prod_subcat) %>% dplyr::summarise(Count = n())
b4 <- ggplot(data = b4_count) + aes(x= Count, y= prod_subcat) + geom_bar(stat = "identity", color = "black", fill = "darkgreen")
b4
```

Q4. Calculate the following information using the merged dataset

a) Time period of the available transaction data

```{r}
min_date <- min(Customer_Final$tran_date)
max_date <- max(Customer_Final$tran_date)
paste("Time period of the available transaction data is", min_date, "to", max_date)
```

b) Count of transactions where the total amount of transaction was negative

```{r}
Transaction_count <- Customer_Final %>% dplyr::group_by(transaction_id) %>% dplyr::summarise(Total = sum(total_amt))

Neg_Transaction_count <- Transaction_count %>% dplyr::filter(Total<0) %>% dplyr::summarise(Count.transaction_id = n())

paste("Count of transaction where the total amount of transaction was negative is", Neg_Transaction_count)
```

Q5. Analyze which product categories are more popular among females vs male customers.

```{r}
require(magrittr)
product_popularity <- Customer_Final %>% dplyr::group_by(Gender,prod_cat) %>% dplyr::summarise(Qty_sum = sum(Qty))
product_popularity <- product_popularity[product_popularity$Gender == "M" | product_popularity$Gender == "F", ]
product_popularity
```

```{r}
paste("Products that are popular among males are:- Books, Electronics, clothing, Home and Kitchen")
```

```{r}
paste("Products that are popoular among females are:- Bags, Footwear")
```

Q6. Which city code has the maximum customers and what was the percentage of customers from that city?

```{r}
City_customers <- Customer_Final %>% dplyr::group_by(city_code) %>% dplyr::summarise(Count.cust_id = n()) %>% dplyr::arrange(desc(Count.cust_id))
City_max_customers <- max(City_customers$Count.cust_id)
City_customers
```   

```{r}
paste("The maximum customers is from the city code 4 and the count is", City_max_customers)
```

```{r}
cust_percentage <- round(City_max_customers / sum(City_customers$Count.cust_id) * 100,2)
paste("The percentage of customers from city code 4 is", cust_percentage, "%")
```

Q7. Which store type sells the maximum products by value and by quantity?

```{r}
Store_type_data <- 	Transactions %>% dplyr::group_by(Store_type) %>% 
  dplyr::summarize(Sum_Amt = sum(Rate), Sum_Qty = sum(Qty))

Store_type_data
```

```{r}
paste("e-Shop store sold the maximum products by value and by quantity")
```

Q8.What was the total amount earned from the "Electronics" and "Clothing" categories from Flagship stores?

```{r}
store_filter <- dplyr::filter(Customer_Final, (prod_cat=="Electronics" | prod_cat== "Clothing") & (Store_type == "Flagship store"))

flag_amt_earned <- store_filter %>% dplyr::group_by(Store_type) %>% dplyr::summarise(total_amt = sum(total_amt))

flag_amt_earned
```

```{r}
paste("The total amount earned from the Electronics and Clothing categories from Flagship stores is", flag_amt_earned$total_amt)
```

Q9. What was the total amount earned from "Male" customers under the "Electronics" category?

```{r}
cat_filter <- dplyr::filter(Customer_Final, Gender == "M" & prod_cat == "Electronics")

male_earning <- cat_filter %>% dplyr::group_by(prod_cat) %>% dplyr::summarise(tot_revenue = sum(total_amt))

male_earning
```

```{r}
paste("The total amount earned from Male customers under the Electronics category is", male_earning$tot_revenue)
```

Q10. How many customers have more than 10 unique transactions, after removing all transactions which have any negative amount?

```{r}
new_cust <- dplyr::filter(Customer_Final, total_amt>0)
unique_trans_cnt <- new_cust %>% dplyr::group_by(cust_id) %>% dplyr::summarise(Count_transaction_id =n())
final_cust_cnt <- unique_trans_cnt %>% dplyr::filter(Count_transaction_id >= 10)
final_cust_cnt
```

```{r}
paste("The customers having more than 10 unique transactions excluding returns are shown above.")
```

Q11. For all customers aged between 25-35, find out:

a) What was the total amount spent for "Electronics" and "Books" product categories?

```{r}
#install.packages('lubridate')
require(lubridate)
diff_date <- as.Date(Customer_Final$DOB, format="%d/%m/%y")
tran_date <- as.Date(Customer_Final$tran_date, format="%d/%m/%y")

Customer_Final <- dplyr::mutate(Customer_Final, Age = (year(tran_date) - year(diff_date)))

q_11 <- Customer_Final %>% dplyr::filter(prod_cat == "Electronics" | prod_cat == "Books")
q_date_filter <- q_11 %>% dplyr::filter((Age>25) & (Age<35))
ques_11 <- q_date_filter %>% dplyr::group_by(prod_cat) %>% dplyr::summarise(Total_amt = sum(total_amt))

ques_11
```

```{r}
paste("The total amount spent for Electronics and Books product categories is 9162360")
```

b) What was the total amount spent by these customers between 1st Jan, 2014 to 1st Mar, 2014?

```{r}
filt <- Customer_Final %>% dplyr::filter((Age>25) & (Age<35))
filt_2 <- filt %>% dplyr::filter(tran_date>=as.Date('2014-01-01', format="%Y-%m-%d") & tran_date<=as.Date('2014-03-01', format="%Y-%m-%d"))
filt_3 <- filt_2 %>% dplyr::summarise(sum_amt = sum(total_amt))

filt_3
```

```{r}
paste("The total amount spent by these customers between 1st Jan, 2014 to 1st Mar, 2014 is", filt_3)
```
