---
title: "Case Study 2 - (Credit Card)"
author: "Mayur Kastiya"
output: html_document
---

------------------------------------

Importing dataset

```{r}
Customer_Acqusition <- read.csv("E:/My Photo/Analytics/R_Bangalore/R Case Studies (All 3 case studies)/R case study 2 (Credit card)/Customer Acqusition.csv")
spend <- read.csv("E:/My Photo/Analytics/R_Bangalore/R Case Studies (All 3 case studies)/R case study 2 (Credit card)/spend.csv")
Repayment <- read.csv("E:/My Photo/Analytics/R_Bangalore/R Case Studies (All 3 case studies)/R case study 2 (Credit card)/Repayment.csv")
```

Data Preparation

Converting "Month" from factor type to date type in "spend" dataframe

```{r}
spend$Month <- as.Date(spend$Month, format="%d-%b-%y")
str(spend)
```

Converting "Month" from factor type to date type in "Repayment" dataframe

```{r}
Repayment$Month <- as.Date(Repayment$Month, format="%d-%b-%y")
str(Repayment)
```

Drop a blank column (missing value) from "Repayment" dataframe

```{r}
Repayment$X <- NULL
```

Drop "No" column from Customer_Acquisition table

```{r}
Customer_Acqusition$No <- NULL
```

Drop "SI.No" column from spend table

```{r}
spend$Sl.No. <- NULL
```

Drop "SL.No" column from Repayment table

```{r}
Repayment$SL.No. <- NULL
```

Drop blank rows (missing values) from "Repayment" dataframe

```{r}
Repayment <- Repayment[-c(1501:1523),]
```

```{r}
head(Customer_Acqusition)
```

```{r}
head(Repayment)
```

```{r}
head(spend)
```

Q1. In the above dataset,

a) In case, age is less than 18, replace it with mean of age values.

```{r}
mean_age <- round(mean(Customer_Acqusition$Age))
Customer_Acqusition$Age <- ifelse(Customer_Acqusition$Age<18,mean_age,Customer_Acqusition$Age)
Customer_Acqusition[(Customer_Acqusition$Age==mean_age),]
```

b) In case spend amount is more than the limit, replace it with 50% of that customer's limit.
(customer's limit provided in acquisition table is the per transaction limit on his card)

```{r}
require(dplyr)
Customer_spend <- dplyr::right_join(Customer_Acqusition,spend,by="Customer")
head(Customer_spend)
```

```{r}
Customer_spend$Amount <- ifelse(Customer_spend$Amount > Customer_spend$Limit, Customer_spend$Limit/2, Customer_spend$Amount)

tail(Customer_spend)
```

c) In case the repayment amount is more than the limit, replace the repayment with the limit.

```{r}
Customer_Repayment <- dplyr::right_join(Customer_Acqusition,Repayment,by="Customer")
head(Customer_Repayment)
```

```{r}
Customer_Repayment$Amount <- ifelse(Customer_Repayment$Amount > Customer_Repayment$Limit, Customer_Repayment$Limit, Customer_Repayment$Amount)

tail(Customer_Repayment)
```

Q2. From the above dataset create the following summaries:

a) How many distinct customers exist?

```{r}
require(magrittr)
Distinct_cust <- length(unique(Customer_Repayment$Customer))
Distinct_cust
```

```{r}
paste("The count of distinct customers is", Distinct_cust)
```

b) How many distinct categories exist?

```{r}
Distinct_prod_cat <- Customer_spend %>% dplyr::group_by(Product) %>% dplyr::summarise(Count.Product = n())

Distinct_prod_cat
```

```{r}
prod_length <- length(Distinct_prod_cat$Product)
paste("The count of distinct categories is", prod_length)
```

c) What is the average monthly spent by customers?

```{r}
Cust_spend_amt <- Customer_spend %>% dplyr::group_by(Customer,Month) %>% dplyr::summarise(Avg_spend = mean(Amount))

require(lubridate)
Cust_spend_amt$Month <- month(Cust_spend_amt$Month)

Avg_monthly_spend <- Cust_spend_amt %>% dplyr::group_by(Customer,Month) %>% dplyr::summarise(Avg_spend = mean(Avg_spend))
head(Avg_monthly_spend,20)

```

d) What is the average monthly repayment by customers?

```{r}
Cust_repayment_amt <- Customer_Repayment %>% dplyr::group_by(Customer,Month) %>% dplyr::summarise(Avg_spend = mean(Amount))

require(lubridate)
Cust_repayment_amt$Month <- month(Cust_repayment_amt$Month)

Avg_monthly_repayment <- Cust_repayment_amt %>% dplyr::group_by(Customer,Month) %>% dplyr::summarise(Avg_spend = mean(Avg_spend))
head(Avg_monthly_repayment,20)
```

e) If the monthly rate of interest is 2.9%, what is the profit for the bank for each month?
(Profit is defined as interest earned on Monthly Profit.)
(Monthly Profit = Monthly repayment - Monthly spend)
Interest is earned only on positive profits and not on negative amounts.

```{r}
Avg_monthly_customers <- dplyr::inner_join(Avg_monthly_spend,Avg_monthly_repayment,by=c("Customer","Month"))

Avg_monthly_customers$Repayment_Month = Avg_monthly_customers$Month
Avg_monthly_customers <- dplyr::rename(Avg_monthly_customers, "Spend_Month" = "Month")
Avg_monthly_customers <- Avg_monthly_customers[,c(1:3,5,4)]

Avg_monthly_customers$Monthly_Profit <- Avg_monthly_customers$Avg_spend.y - Avg_monthly_customers$Avg_spend.x

Avg_monthly_customers$Profit <- ifelse(Avg_monthly_customers$Monthly_Profit>0, (Avg_monthly_customers$Monthly_Profit*2.9)/100, NA)
Avg_monthly_customers <- Avg_monthly_customers[,c(1:5,7,6)]

head(Avg_monthly_customers,10)
```

f) What are top 5 product types?

```{r}
Prod_types <- Customer_spend %>% dplyr::group_by(Type) %>% dplyr::summarise(Amt_Total = sum(Amount)) %>% dplyr::arrange(desc(Amt_Total))

head(Prod_types,5)
```

g) Which city is having maximum spend?

```{r}
City_Types <- Customer_spend %>% dplyr::group_by(City) %>% dplyr::summarise(Amt_Total = sum(Amount)) %>% dplyr::arrange(desc(Amt_Total))

head(City_Types,1)
```

h) Which age group is spending more money?

```{r}
Customer_spend$Age_Group <- ifelse(((Customer_spend$Age > 18) & (Customer_spend$Age <25)), "Youth", ifelse(((Customer_spend$Age >=25) & (Customer_spend$Age <65)), "Adult", "Senior"))

People_category <- Customer_spend %>% dplyr::group_by(Age_Group) %>% dplyr::summarise(Money_Spend = sum(Amount)) %>% dplyr::arrange(desc(Money_Spend))

People_category
```

```{r}
paste("The Adults aged between 25 to 65 are spending more money.")
```

i) Who are the top 10 customers in terms of repayment?

```{r}
Top_repayment_customers <- Customer_Repayment %>% dplyr::group_by(Customer) %>% dplyr::summarise(Repayment_Amt = sum(Amount)) %>% dplyr::arrange(desc(Repayment_Amt))

head(Top_repayment_customers,10)
```

Q3. Calculate the city wise spend on each product on yearly basis. Also include a graphical representation for the same.

```{r}
Customer_spend$Yearly_Spend <- year(Customer_spend$Month)

#install.packages("reshape2")
require(reshape2)

City_wise_spend <- Customer_spend %>% dplyr::group_by(Product,City,Yearly_Spend) %>% dplyr::summarise(Amount = sum(Amount))

Reshape_City_wise_spend <- reshape2::dcast(City_wise_spend, City~Product+Yearly_Spend)

Reshape_City_wise_spend
```

```{r}
require(ggplot2)
options(scipen = 999)
City_wise_spend$Yearly_Spend <- as.factor(City_wise_spend$Yearly_Spend)
Stacked_Bar <- ggplot(City_wise_spend) + aes(x = Amount, y= City, fill=Product) + geom_bar(stat = "identity") + facet_grid(. ~ Yearly_Spend)

Stacked_Bar
```

Q4. Create graphs for

a) Monthly comparison of total spends, city wise

```{r}
options(scipen = 999)
Customer_spend$Monthly_Spend <- month(Customer_spend$Month)
Customer_spend$Monthly_Spend <- as.factor(Customer_spend$Monthly_Spend)

Monthly_comparison <- ggplot(Customer_spend) + aes(x = Amount, y= City, fill=Monthly_Spend) + geom_bar(stat = "identity")

Monthly_comparison
```

b) Comparison of yearly spend on air tickets

```{r}
Spend_Type <- Customer_spend %>% dplyr::group_by(Type,Yearly_Spend) %>% dplyr::summarise(Sum = sum(Amount))

Air_Ticket <- head(Spend_Type,3)

Air_Ticket$Labels <- paste(Air_Ticket$Sum, " (", Air_Ticket$Yearly_Spend, ")")

pie(Air_Ticket$Sum, Air_Ticket$Labels, col = rainbow(length(Air_Ticket$Sum)), main = "Comparison of yearly spend on Air Tickets")

```

c) Comparison of monthly spend on each product (look for any seasonabilty that exists in terms
of spend)

```{r}
options(scipen = 999)
Customer_spend$Yearly_Spend <- as.factor(Customer_spend$Yearly_Spend)

Prod_Monthly_comparison <- ggplot(Customer_spend) + aes(x = Product, y= Amount, fill=Monthly_Spend) + geom_bar(stat = "identity", position = "dodge") + facet_grid(Yearly_Spend ~ .)

Prod_Monthly_comparison
```

Q5. Write user defined R function to perform the following analysis:

You need to find top 10 customers for each city in terms of their repayment amount by different
products and by different time periods i.e. year or month. The user should be able to specify
the product (Gold/Silver/Platinum) and time period (yearly or monthly) and the function should
automatically take these inputs while identifying the top 10 customers.

```{r}
Customer_Repayment$Yearly <- year(Customer_Repayment$Month)
Customer_Repayment$Monthly <- month(Customer_Repayment$Month)

Product_category <- readline(prompt="Enter Product Category and product category should be in Gold/Silver/Platinum: ")
  
Time_period <- readline(prompt="Enter Time Period and time period should be in yearly/monthly: ")

Top_10_Customers <- function(Product_category,Time_period){
  
  top_10 <- Customer_Repayment %>% dplyr::group_by(Customer,City,Product,Yearly) %>% dplyr::summarise(Amount = sum(Amount)) %>% dplyr::arrange(desc(Amount))
  
  top_output <- top_10 %>% dplyr::filter((Product == Product_category) & (Yearly == Time_period))
  
  return(head(top_output,10))
}

Top_10_Customers(Product_category =  "Gold",Time_period =  "2006")
```

NOTE - The user can pass the inputs for Products and Year but as of now, I have passed a default arguments as "Gold" and "2006" into the function to show the output in R Markdown report.
