---
title: "Case Study 3 - (Visualization)"
author: "Mayur Kastiya"
output: html_document
---

----------------------------------------------

Importing dataset

```{r}
SalesData <- read.csv("E:/My Photo/Analytics/R_Bangalore/R Case Studies (All 3 case studies)/R case study 3 (Visualization)/SalesData.csv")

head(SalesData)
```

```{r}
str(SalesData)
```

Q1. Compare Sales by region for 2016 with 2015 using bar chart

```{r}
require(ggplot2)
require(tidyr)
options(scipen = 999)

Region_sales <- SalesData %>% gather(SalesYear,Sales,Sales2015:Sales2016) %>% dplyr::group_by(Region,SalesYear) %>% dplyr::summarise(Sum = sum(Sales))

Sales_Comparison <- ggplot(Region_sales) + aes(x = Region, y= Sum, fill=SalesYear) + geom_bar(stat="identity", position=position_dodge())+ geom_text(aes(label=round(Sum)))

Sales_Comparison

```

Q2. Pie charts for sales for each region is 2016

```{r}
Region_2016_Pie <- Region_sales %>% dplyr::filter(SalesYear == "Sales2016")

pie(x = Region_2016_Pie$Sum, labels = Region_2016_Pie$Region, main = "Pie Chart of Sales 2016")
```

```{r}
pct <- prop.table(Region_2016_Pie$Sum) * 100
lbl <- paste0(round(pct,1),"%")

pie(Region_2016_Pie$Sum, labels = paste(lbl,":",Region_2016_Pie$Region), col = rainbow(length(Region_2016_Pie$Sum)), main = "Pie chart of sales 2016")
```

```{r}
require(plotrix)
pie3D(Region_2016_Pie$Sum, labels = paste(lbl,":",Region_2016_Pie$Region), col = rainbow(length(Region_2016_Pie$Sum)), explode = 0.1, main = "Pie chart of sales 2016")
```

Q3. Compare sales of 2015 and 2016 with Region and Tiers

```{r}
Region_Tier_Sales <- SalesData %>% gather(SalesYear,Sales,Sales2015:Sales2016) %>% dplyr::group_by(Region,Tier,SalesYear) %>% dplyr::summarise(Sales = sum(Sales))

Region_Tier_Bar <- ggplot(Region_Tier_Sales) + aes(x = Tier, y= Sales, fill=SalesYear) + geom_bar(stat = "identity", position = "dodge") + facet_grid(. ~ Region)

Region_Tier_Bar
```

Q4. In East region, which state registered a decline in 2016 as compared to 2015?

```{r}
East_Region_Sales <- SalesData %>% gather(SalesYear,Sales,Sales2015:Sales2016) %>% dplyr::filter(Region == "East") %>% dplyr::group_by(Region, SalesYear, State) %>% dplyr::summarise(Sales = sum(Sales))

East_Region_Bar <- ggplot(East_Region_Sales) + aes(x = State, y= Sales, fill=SalesYear) + geom_bar(stat = "identity", position = "dodge")

East_Region_Bar
```

```{r}
paste("In East region, NY registered a decline in Sales in 2016")
```

Q5. In all the High tier, which division saw a decline in number of units sold in 2016 compared to 2015?

```{r}
High_Tier_Units <- SalesData %>% gather(Year,Units,Units2015:Units2016) %>% dplyr::filter(Tier == "High") %>% dplyr::group_by(Year, Division) %>% dplyr::summarise(Units = sum(Units))

High_Tier_Bar <- ggplot(High_Tier_Units) + aes(x = Units, y= Division, fill=Year) + geom_bar(stat = "identity", position = "dodge")

High_Tier_Bar
```

```{r}
paste("There is no division which saw a decline in number of units sold in 2016 compared to 2015 for High tier")
```

Q6. Create a new column Qtr -
Jan-Mar : Q1
Apr-Jun : Q2
Jul-Sep : Q3
Oct-Dec : Q4

```{r}
SalesData$Qtr <- ifelse((SalesData$Month == "Jan" | SalesData$Month == "Feb" | SalesData$Month == "Mar"), "Q1", ifelse((SalesData$Month == "Apr" | SalesData$Month == "May" | SalesData$Month == "Jun"), "Q2", ifelse((SalesData$Month == "Jul" | SalesData$Month == "Aug" | SalesData$Month == "Sep"), "Q3", "Q4")))
```

Q7. Compare Qtr wise sales in 2015 and 2016 in a bar plot

```{r}
Qtr_wise_Sales <- SalesData %>% gather(SalesYear,Sales,Sales2015:Sales2016) %>% dplyr::group_by(Qtr,SalesYear) %>% dplyr::summarise(Sales = sum(Sales))

Qtr_wise_Bar <- ggplot(Qtr_wise_Sales) + aes(x = Qtr, y= Sales, fill=SalesYear) + geom_bar(stat = "identity", position = "dodge")

Qtr_wise_Bar
```

Q8. Determine the compostion of Qtr wise sales in 2015 with regards to all tiers in a pie chart. (Draw 4 pie charts representing a Quarter for each tier)

```{r}
Qtr_wise_tier <- SalesData %>% gather(SalesYear,Sales,Sales2015:Sales2016) %>% dplyr::group_by(Qtr,Tier,SalesYear) %>% dplyr::summarise(Sales = sum(Sales)) %>% dplyr::filter(SalesYear == "Sales2015")

Q1 <- Qtr_wise_tier %>% dplyr::filter(Qtr == "Q1")
Q2 <- Qtr_wise_tier %>% dplyr::filter(Qtr == "Q2")
Q3 <- Qtr_wise_tier %>% dplyr::filter(Qtr == "Q3")
Q4 <- Qtr_wise_tier %>% dplyr::filter(Qtr == "Q4")
```

```{r}
pie(x = Q1$Sales, labels = Q1$Tier, main = "Qtr1")
```

```{r}
pie(x = Q2$Sales, labels = Q2$Tier, main = "Qtr2")
```

```{r}
pie(x = Q3$Sales, labels = Q3$Tier, main = "Qtr3")
```

```{r}
pie(x = Q4$Sales, labels = Q4$Tier, main = "Qtr4")
```

